%-------------------------
% Resume in Latex (One-Page Version)
% Author : Tianyi Zhang
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.55in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

\pdfgentounicode=1

%-------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{%
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumePublication}[1]{
  \item\small{#1 \vspace{-1pt}}
}

\newcommand{\resumeKeywords}[1]{
  \vspace{2pt}\item[]\small{\textit{Keywords: #1}}\vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2.5pt, topsep=3pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Tianyi Zhang} \\ \vspace{2pt}
    \small 404-422-2842 $|$ \href{mailto:tzhang708@gatech.edu}{tzhang708@gatech.edu} $|$
    \href{https://www.linkedin.com/in/tianyi-zhang2002/}{LinkedIn} $|$
    \href{https://scholar.google.com/citations?hl=en&view_op=list_works&user=46rbYk0AAAAJ}{Google Scholar}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science}{Aug 2025 -- Dec 2026}
    \resumeSubheading
      {Emory University}{Atlanta, GA}
      {Bachelor of Science in Quantitative Sciences}{Aug 2021 -- May 2025}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {LinkedIn Corporation}{Mountain View, CA}
    {AI/ML Engineer Intern $|$ GenAI for RecSys, LLM Post-Training}{May 2026 -- Present}
\resumeItemListStart
  \resumeItem{Contributing to LinkedIn's \textbf{out-of-network retrieval} system for homepage-feed candidate generation, applying \textbf{LLM-based generative retrieval} to surface relevant content beyond a member's immediate network.}

  \resumeItem{Led a research direction on \textbf{adaptive and compressed member representation}---modeling profile signals, temporal engagement history, long-history compression, and member-regime differences in retrieval.}

  \resumeItem{Built a \textbf{multi-axis retrieval experimentation framework} mapping tradeoffs among \textbf{Recall@K}, diversity, efficiency, and evaluation fidelity across cold-start, sparse, stale, and active-user regimes.}

  \resumeItem{Developed a reusable \textbf{out-of-network experimentation pipeline}---standardized training, retrieval evaluation, config reuse, execution tracking, and experiment logging---improving team velocity and reproducibility for LLM retrieval research.}
\resumeItemListEnd

  \resumeSubheading
    {Georgia Tech Efficient \& Intelligent Computing Lab $\cdot$ NVIDIA Collaboration}{Atlanta, GA}
    {Student Researcher $|$ LLM Evaluation, Agentic AI}{Jul 2025 -- Dec 2025}
  \resumeItemListStart
    \resumeItem{Co-authored \textbf{AgentSuite} (\textbf{ICML 2026}), an automated pipeline auditing validity flaws in LLM-agent benchmarks; matched expert judgments at \textbf{0.79--0.87 F1} across \textbf{6 benchmarks} and showed flaws affect \textbf{$\sim$23\% of tasks}, reshuffling \textbf{63\% of model rankings} on a 30-LLM leaderboard.}
    \resumeItem{Built the pipeline's \textbf{taxonomy-guided LLM-judge} and \textbf{rule-based structural detectors}, which decompose an agent task into user, environment, ground-truth, and evaluation components; generalized to unseen benchmarks with no retuning, surfacing \textbf{100+} undocumented issues.}
  \resumeItemListEnd


\resumeSubheading
    {Emory Graph Mining Lab}{Atlanta, GA}
    {Machine Learning Researcher $|$ AI for Science, Graph Representation Learning}{Dec 2023 -- May 2025}
  \resumeItemListStart
    \resumeItem{First-authored a \textbf{causal brain-connectivity} method (\textbf{AIME 2025}) that recovered \textbf{directional} dependencies invisible to correlation-based graphs, improving downstream diagnostic prediction across \textbf{$\sim$8K patients} via Granger-directed graphs.}
    \resumeItem{Co-authored a \textbf{state-based Transformer} (\textbf{IEEE EMBC 2025}, oral) that modeled temporal transitions across latent functional-connectivity states, outperforming static-connectivity baselines on clinical prediction.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=3.5pt, topsep=3pt]
  \resumePublication{H. Suh*, S. Lee*, B. Ji*, R. Khare, B. Khan, H. Kim, \textbf{T. Zhang}, et al. ``\href{https://openreview.net/pdf?id=2Exmr1eIKZ}{AgentSuite: Toward More Reliable Agent Evaluation with a Component-Based
Benchmark Auditing Pipeline}'' \textit{International Conference on Machine Learning} (\textbf{ICML}) 2026.}
  \resumePublication{\textbf{T. Zhang}, K. Han, J. Nie, et al. ``\href{https://link.springer.com/chapter/10.1007/978-3-031-95841-0_81}{Causal Brain Connectivity: Integrating Granger Directed Graphs in fMRI Analysis}.'' \textit{International Conference on Artificial Intelligence in Medicine} (\textbf{AIME}) 2025.}
  \resumePublication{J. Nie, K. Han, \textbf{T. Zhang}, et al. ``\href{https://www.cs.emory.edu/~jyang71/files/bnst.pdf}{Brain Network State Transformer: Leveraging State Functional Connectivity}.'' \textit{IEEE Engineering in Medicine and Biology Society} (\textbf{EMBC}) 2025. \textit{(Oral)}}
\end{itemize}

%-----------PROJECTS & OPEN SOURCE-----------
\section{Projects \& Open Source}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{CoAct}: Governance Substrate for Two Coding Agents \small{\href{https://github.com/tianyi-zhang-02/coact}{\faGithub}}}{Jul 2026 -- Present}
    \resumeItemListStart
      \resumeItem{A dependency-free \textbf{Go} binary that lets Claude Code and Codex work in one repository safely, coordinating through the filesystem instead of the token stream---capability policies, advisory locks, and a shared task board.}
      \resumeItem{Isolates each agent in its own \textbf{worktree} behind merge gates and keeps an \textbf{append-only journal} for replayable oversight; organized around \textbf{security, controllability, and cost}.}
    \resumeItemListEnd
    \resumeProjectHeading{\textbf{NVIDIA NeMo RL}: Open-Source Contributor \small{\href{https://github.com/NVIDIA-NeMo/RL}{\faGithub}}}{2026}
    \resumeItemListStart
      \resumeItem{Contributor to NVIDIA's open-source library for \textbf{reinforcement learning and post-training} of large language models.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming:} Python, Go, SQL, Java, R, C/C++ \quad
    \textbf{ML/AI:} PyTorch, CUDA, Hugging Face, vLLM,  SGLang, LangChain, MLflow \quad
    \textbf{Infra:} Docker, AWS, GitHub Actions, FastAPI, Linux \quad
    \textbf{Data:} PostgreSQL, MongoDB, Redis, Apache Spark
  }}
\end{itemize}

\end{document}